The Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2014-03-07 papers/pair-correlation/paper.tex

\section{Our approach}
%% We approximate the pair correlation with the average of two radial
%% distribution functions, evaluated at the distance between the two
%% points, that are themselves functions of the averaged pair correlation
%% at contact $g_{\sigma}(\rr)$ discussed above~\cite{schulte2012using},
%% evaluated at the two points.
In the approaches for the pair distribution function mentioned above,
the radial distribution function used to approximate pair correlation
was dependent upon the density averaged over some volume.  We seek to
achieve greater accuracy by using instead a function dependent upon
our averaged $g_{\sigma}(\rr)$ discussed above, which holds more
information about an inhomogeneous system than does a simple
convolution of the density.
%
We approximate the pair correlation with the average of two radial
distribution functions, evaluated at the distance between the two
points, that are themselves functions of the averaged pair correlation
at contact $g_{\sigma}(\rr)$ evaluated at the two points:
%
%% We therefore seek a function form
%% for our radial distribution that is dependent upon $g_{\sigma}(\rr)$
%% and that will approach the correct solution in the homogeneous limit
%% and also in the limit of contact distance between the two points.
\begin{align}
  g^{(2)}(\rr_1,\rr_2) = \frac{g(|r_{12}|, g_\sigma(\rr_1)) +
    g(|r_{12}|, g_\sigma(\rr_2))}{2}. \label{eq:g2-our-mean}
\end{align}
This approximation is constructed to reproduce the exact value for the
integral$ \int n(\rr_1)n(\rr_2)
g^{(2)}(\rr_1,\rr_2)\delta(|\rr_1-\rr_2|-\sigma)d\rr_1d\rr_2$.  This
approximation (described in Eq.~\ref{eq:g2-our-mean}) requires the
radial distribution function as a function of $r$ and $g_\sigma$.  One
approach is to compute $\eta$ from $g_\sigma$ and then find
$g(r,\eta)$ either using some approximate functional form
(e.g. Percus-Yevick) or using Monte Carlo simulation results.  In this
paper we use the latter (also for evaluating the approximations of
earlier works), and refer to this approximation (with an exact
$g(r,g_\sigma)$) as ``this work MC.''

>>>>

\section{Our approach}
%% We approximate the pair correlation with the average of two radial
%% distribution functions, evaluated at the distance between the two
%% points, that are themselves functions of the averaged pair correlation
%% at contact $g_{\sigma}(\rr)$ discussed above~\cite{schulte2012using},
%% evaluated at the two points.
In the approaches for the pair distribution function mentioned above,
the radial distribution function used to approximate pair correlation
was dependent upon the density averaged over some volume.  We seek to
achieve greater accuracy by using instead a function dependent upon
our averaged $g_{\sigma}(\rr)$ discussed above, which holds more
information about an inhomogeneous system than does a simple
convolution of the density.
%
We approximate the pair correlation with the average of two radial
distribution functions, evaluated at the distance between the two
points, that are themselves functions of the averaged pair correlation
at contact $g_{\sigma}(\rr)$ evaluated at the two points:
%
%% We therefore seek a function form
%% for our radial distribution that is dependent upon $g_{\sigma}(\rr)$
%% and that will approach the correct solution in the homogeneous limit
%% and also in the limit of contact distance between the two points.
\begin{align}
  g^{(2)}(\rr_1,\rr_2) = \frac{g(|r_{12}|, g_\sigma(\rr_1)) +
    g(|r_{12}|, g_\sigma(\rr_2))}{2}. \label{eq:g2-our-mean}
\end{align}
This approximation is constructed to reproduce the exact value for the
integral$ \int n(\rr_1)n(\rr_2)
g^{(2)}(\rr_1,\rr_2)\delta(|\rr_1-\rr_2|-\sigma)d\rr_1d\rr_2$.  This
approximation (described in Eq.~\ref{eq:g2-our-mean}) requires the
radial distribution function as a function of $r$ and $g_\sigma$.  One
approach is to compute $\eta$ from $g_\sigma$ and then find
$g(r,\eta)$ either using some approximate functional form
(e.g. Percus-Yevick) or using Monte Carlo simulation results.  In this
paper we use the latter (also for evaluating the approximations of
earlier works), and refer to this approximation (with an exact
$g(r,g_\sigma)$) as ``this work MC.''  \fixme{We should develop
  separate acroyms for each method.}
